<!-- R Commander Markdown Template -->

gowtham 
=======================

### Mr. Royal

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

```{r}
Dataset <- readXL("C:/Users/Mr. Royal/Downloads/BComCA.xlsx", rownames=FALSE, header=TRUE, na="", sheet="B.COM CA",
   stringsAsFactors=TRUE)
```

```{r}
library(abind, pos=16)
```


```{r}
library(e1071, pos=17)
```



### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"X12th.Marks", drop=FALSE], statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,.25,
  .5,.75,1))
```


### Histogram: X12th.Marks
```{r}
with(Dataset, Hist(X12th.Marks, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"PercentageMarks", drop=FALSE], statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,
  .25,.5,.75,1))
```
# intrepertation:
-The Average score of the students who joined BCom CA is 65%
-50% of the students, scored more than 65% of marks in their 12th Std.
-Top 25% of the students scored more than 73% of marks in their 12th Std.



### Histogram: PercentageMarks
```{r}
with(Dataset, Hist(PercentageMarks, scale="frequency", breaks="Sturges", col="darkgray"))
```

```{r}
Dataset <- readXL("C:/Users/Mr. Royal/Downloads/BSc IT.xlsx", rownames=FALSE, header=TRUE, na="", sheet="B.SC IT", 
  stringsAsFactors=TRUE)
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"PercentageMarks", drop=FALSE], statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,
  .25,.5,.75,1))
```
# Interpretation:

-The Average score of the students who joined B.Sc IT is 64%
50% of the students, scored more than 64% of marks in their 12th Std.
Top 25% of the students scored more than 71% of marks in their 12th Std.
 

### Histogram: PercentageMarks
```{r}
with(Dataset, Hist(PercentageMarks, scale="frequency", breaks="Sturges", col="darkgray"))
```

```{r}
Dataset <- readXL("C:/Users/Mr. Royal/Downloads/CombinedITCA (1).xlsx", rownames=FALSE, header=TRUE, na="", 
  sheet="MergedDataset", stringsAsFactors=TRUE)
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"X12th.Marks", drop=FALSE], statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,.25,
  .5,.75,1))
```


### Dot Plot: X12th.Marks
```{r}
with(Dataset, Dotplot(X12th.Marks, bin=FALSE))
```


### Histogram: X12th.Marks
```{r}
with(Dataset, Hist(X12th.Marks, scale="frequency", breaks="Sturges", col="darkgray"))
```

```{r}
Dataset <- readXL("C:/Users/Mr. Royal/Downloads/BSc IT.xlsx", rownames=FALSE, header=TRUE, na="", sheet="B.SC IT", 
  stringsAsFactors=TRUE)
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"X12th.Marks", drop=FALSE], groups=Dataset$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


### Histogram: X12th.Marks
```{r}
with(Dataset, Hist(X12th.Marks, groups=Gender, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"X12th.Marks", drop=FALSE], groups=Dataset$PgmName, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


### Boxplot: X12th.Marks ~ PgmName
```{r}
Boxplot(X12th.Marks ~ PgmName, data=Dataset, id=list(method="y"))
```


### Plot of Means: X12th.Marks by PgmName
```{r}
with(Dataset, plotMeans(X12th.Marks, PgmName, error.bars="se", connect=TRUE))
```

```{r}
Dataset <- readXL("C:/Users/Mr. Royal/Downloads/BSc IT.xlsx", rownames=FALSE, header=TRUE, na="", sheet="B.SC IT", 
  stringsAsFactors=TRUE)
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"X12th.Marks", drop=FALSE], groups=Dataset$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


### Histogram: X12th.Marks
```{r}
with(Dataset, Hist(X12th.Marks, groups=Gender, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Boxplot: X12th.Marks ~ Gender
```{r}
Boxplot(X12th.Marks ~ Gender, data=Dataset, id=list(method="y"))
```


### Plot of Means: X12th.Marks by Gender
```{r}
with(Dataset, plotMeans(X12th.Marks, Gender, error.bars="se", connect=TRUE))
```

```{r}
Dataset <- readXL("C:/Users/Mr. Royal/Downloads/BComCA.xlsx", rownames=FALSE, header=TRUE, na="", sheet="B.COM CA",
   stringsAsFactors=TRUE)
```


### Numerical Summaries: Dataset
```{r}
numSummary(Dataset[,"X12th.Marks", drop=FALSE], groups=Dataset$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


### Histogram: X12th.Marks
```{r}
with(Dataset, Hist(X12th.Marks, groups=Gender, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Boxplot: X12th.Marks ~ Gender
```{r}
Boxplot(X12th.Marks ~ Gender, data=Dataset, id=list(method="y"))
```


### Plot of Means: X12th.Marks by Gender
```{r}
with(Dataset, plotMeans(X12th.Marks, Gender, error.bars="se", connect=TRUE))
```

```{r}
library(colorspace, pos=18)
```



### Pie Chart: Gender
```{r}
with(Dataset, piechart(Gender, xlab="", ylab="", main="Gender", col=rainbow_hcl(2), scale="percent"))
```

```{r}
Dataset <- readXL("C:/Users/Mr. Royal/Downloads/CombinedITCA (1).xlsx", rownames=FALSE, header=TRUE, na="", 
  sheet="MergedDataset", stringsAsFactors=TRUE)
```


### Boxplot: X12th.Marks ~ Gender
```{r}
Boxplot(X12th.Marks ~ Gender, data=Dataset, id=list(method="y"))
```


### Independent-Samples t-Test: X12th.Marks ~ Gender
```{r}
t.test(X12th.Marks ~ Gender, alternative = "two.sided", conf.level = .95, var.equal = FALSE, data = Dataset)
```


### Pie Chart: Gender
```{r}
with(Dataset, piechart(Gender, xlab="", ylab="", main="Gender", col=rainbow_hcl(2), scale="percent"))
```

