
```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

```{r}
load("C:/Users/User/Downloads/assignment-1 (1).Rmd")
```


```{r}
Assignment <- readXL("C:/Users/User/Downloads/CombinedITCA.xlsx", rownames=FALSE, header=TRUE, na="", sheet="MergedDataset", stringsAsFactors=TRUE)
```


```{r}
library(abind, pos=16)
```


```{r}
library(e1071, pos=17)
```



### Numerical Summaries: Assignment
```{r}
numSummary(Assignment[,"X12th.Marks", drop=FALSE], groups=Assignment$Gender, statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


### Single-Sample t-Test: X12th.Marks
```{r}
with(Assignment, (t.test(X12th.Marks, alternative = "two.sided", mu = 0.0, conf.level = .95)))
```


### Independent-Samples t-Test: X12th.Marks ~ Gender
```{r}
t.test(X12th.Marks ~ Gender, alternative = "two.sided", conf.level = .95, var.equal = FALSE, data = Assignment)
```


### Boxplot: X12th.Marks ~ Gender
```{r}
Boxplot(X12th.Marks ~ Gender, data=Assignment, id=list(method="y"))
```


### Numerical Summaries: Assignment
```{r}
numSummary(Assignment[,"X12th.Marks", drop=FALSE], groups=Assignment$Gender, statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,.25,.5,.75,1))
```


### Linear Model: RegModel.1: X12th.Marks~PercentageMarks
```{r}
RegModel.1 <- lm(X12th.Marks~PercentageMarks, data=Assignment)
summary(RegModel.1)
```


### Frequencies: Gender
```{r}
local({
  .Table <- with(Assignment, table(Gender))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
})
```


### Correlation Test: PercentageMarks, X12th.Marks
```{r}
with(Assignment, cor.test(PercentageMarks, X12th.Marks, alternative="two.sided", method="pearson"))
```


### Frequencies: Board, Gender
```{r}
local({
  .Table <- with(Assignment, table(Board))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
})
local({
  .Table <- with(Assignment, table(Gender))
  cat("\ncounts:\n")
  print(.Table)
  cat("\npercentages:\n")
  print(round(100*.Table/sum(.Table), 2))
})
```


### Linear Model: RegModel.2: X12th.Marks~PercentageMarks
```{r}
RegModel.2 <- lm(X12th.Marks~PercentageMarks, data=Assignment)
summary(RegModel.2)
```


### Chi-Squared Quantiles
```{r}
qchisq(c(0.05), df=95, lower.tail=TRUE)
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Gender, mean, na.action=na.omit, data=Assignment) # mean by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Gender, median, na.action=na.omit, data=Assignment) # median by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Gender, sd, na.action=na.omit, data=Assignment) # sd by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Gender, var, na.action=na.omit, data=Assignment) # var by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Gender, CV, na.action=na.omit, data=Assignment) # CV by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Board, mean, na.action=na.omit, data=Assignment) # mean by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Board, median, na.action=na.omit, data=Assignment) # median by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Board, sd, na.action=na.omit, data=Assignment) # sd by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Board, var, na.action=na.omit, data=Assignment) # var by groups
```



### Table of Summary Statistics: PercentageMarks
```{r}
Tapply(PercentageMarks ~ Board, CV, na.action=na.omit, data=Assignment) # CV by groups
```


